A quantitative framework for investigating the reliability of empirical network construction: supplemental information

### 2019-01-16 manuscript/reply_to_reviewers.tex

		\textbf{R:} We agree with the Reviewer that a full simulation study, based on recreating the sources of uncertainty in a data set generated from known processes, is a good way to demonstrate the power of a novel method. The novelty and impact of our work, however, is not in the method itself (several other Reviewers rightly point out that similar approaches have occasionally been used before) but in connecting a Bayesian statistical approach to the problem of limited and uneven sampling of networks and, we hope, in making this method more accessible to those without extensive statistical or modelling experience. In other words, what we try to achieve here is to alert empirical ecologists constructing and analysing networks to the uncertainties built into their work. We then try to provide them with simple tools for grasping the extent and consequences of typical patterns. Please note that other Reviewers (as expressed by Reviewer 3 in particular) find this a highly worthwhile objective.

@@

		What Reviewer 2 proposes would be more suitable for an entirely novel method and is substantially beyond the scope of the present study. There is indubitably a place for simulation studies in order to find the most powerful method once a variety of tools are in common use, especially for researchers aiming to convince modellers that their tool is more powerful. Our manuscript, however, is not aimed at those already comfortable with Bayesian approaches but rather at those who may be aware of the problems of uneven uncertainty but not aware of any way to include this information in their analyses. We are confident that even a very simple model which incorporates the differences in sampling across interactions (as ours does) is more powerful than a model which ignores this information completely, and we therefore do not intend to conduct a full-scale simulation study. We accept that this means that those already using more intricate Bayesian methods are unlikely to switch to our simpler version; it was never our intention that they should do so.

		We must also point out that some of the Reviewer's questions (e.g., how much data is necessary to expect good results) have already been answered analytically. Without an informative prior, we need approximately 35 observed co-occurrences with no observed interaction to be 95\% confident that the interaction does not occur. We also provide simple R code that will allow interested readers to analytically explore the response of confidence intervals, etc. to different amounts of data and different strengths of priors. While a simulation study could help to develop intuitions about changing field conditions, these analytical responses are exact and more general.

	5. Request for an extended results and discussion section

		\begin{refquote}
			5/ results\&discussion too short: the reader is surprised to read 27 lines of raw results only... Given the amount of new methodology that is proposed, one can expect a complete description of its pros and cons. Obviously, a simulation study (see above) would enrich the results part. Forgetting about the length of these parts, it is still difficult to catch the key messages from the text, and it is not obvious to relate discussion and the obtained results (for instance,from l.343 to l.351).
		\end{refquote}

@@

		\textbf{R:} We very much appreciate the Reviewer's point that the results and discussion do not clearly illustrate the point of the manuscript. Although we have not conducted a simulation study (see above), we have extensively revised these sections in order to highlight the main thread through the manuscript. Due to space limitations, we were unable to greatly expand either section (we prioritise the introduction and methods, which lay out the problem of uncertainty in networks and how it can be partially addressed), but we hope that the results now more clearly demonstrate how a Bayesian approach can address the uncertainty inherent in sampling.

	6. Suggestions to improve notation

		\begin{refquote}
			6/ lack of rigorous notations: it is possible to understand the approach with the present notations but some improvements can help the reader because there are a series of inconsistencies. Here are some suggestions. The authors chose upper case letters L,T ,X,D for single entities whereas the mathematician is used to expect matrices or constants in upper case. Traditionally, given species i and j, we would consider interaction $L_ij$, feasibility $X_ij$, detection ability $D_ij$... \\
			Still, what is T?? not defined, never reused: is it a characteristics on i, on j, on both? \\
			How can be D<1 on l.169? D=0 or 1 since it says if an interaction is detectable or not... \\
			Moreover, L is reused later but is the number of interactions (l.100 supp.mat)... \\
			What is ``N'' in Figure 4? is it ``n''? What is $n_ij$ and $k_ij$ l.266? Never defined, never reused. \\
			In the beginning of the paper, $\lambda$ is a probability (l.62) but it becomes a random variable (l.164): it would be more consistent to introduce before the notion of hyperparameters  (l.209-213) and to explain we consider that $\lambda$ is drawn into its distribution.
		\end{refquote}

@@

		\textbf{R:} 
			\begin{itemize}
				\item As described above, we have now indexed $L$, $T$, $X$, $D$, etc. by $ij$. 
				\item $T$ describes trait matching, so it is a characterisation on $i$ and $j$ together. 
				\item $D$ can be \textless1 because some interactions are detectable but with a lower probability due to limitations in sampling techniques, sampling time, etc. With infinite monitoring time and capacity, all $D_{ij}$ would indeed be 0 or 1, but given real-world constraints that lead to otherwise-detectable interactions being missed, we feel it makes sense to discuss $0<D_{ij}<1$. For instance, consider a predator feeding upon two prey. If one of the prey (A) has many hard parts and is digested slowly, while the other has no hard parts and is digested quickly (B), the interaction involving prey A will be more detectable than the interaction involving prey B. The interaction with prey B is does not have D=0, because the interaction might be observed directly or through examination of gut contents very soon after B was consumed, but we cannot say that D=1 because we are quite likely not to detect this interaction in any given sample. 
				\item Using L to mean the number of interactions is incredibly common in the food-web literature, especially when defining connectance (as in the instance the Reviewer points out - now included in the main text). That said, we appreciate that this useage may confuse mathematicians. We therefore now define the number of interactions as N and hope that this is less puzzling.
				\item Yes, the N on figure 4 should have been $n_{ij}$. This has been corrected. As discussed above, $n$ and $k$ are now always indexed by $ij$. 
				\item We do not catch what the Reviewer is aiming at here. We hope that our revised introduction and methods have addressed this point; if not, we request that the Reviewer kindly provide some more detail so that we can address his/her concern.
			\end{itemize}

	7. l.62: define formally T

		\textbf{R}: We now define $T_{ij}$ as ``some function describing trait-matching $\mathbf{T_{ij}}$``. This definition is intentionally open-ended as we foresee that $T_{ij}$ could be binary (traits are compatible or not) or continuous with a wide array of distributions.

	8. Clarify the point of analysing the data using an alternative prior

		\begin{refquote}	
			-l.244: this is weird to mention that the analysis has been done on another dataset but that the results will not be discussed... What is the interest for the reader?
		\end{refquote}

@@

		\textbf{R}: We have removed the reference to the analysis and now explain more thoroughly how the choice of an unsuitable prior can result in unrealistic posterior distributions, as this is the interest for the reader.

	9. No ``moral network''

		\begin{refquote}
			-l.149: since the authors consider the interactions are independent, there is morally no network in the approach (except the result)
		\end{refquote}

		\textbf{R:} While we do implicitly consider interactions independent, we disagree that there is no network in the approach. The structure of the network is used to design our prior distribution for interaction probabilities, and we show how an understanding of uncertainty at the level of species pairs is essential to understand uncertainty about network-level properties (Appendix S10). Note that even had we specifically stated that interactions are considered independent, this would not be unique among network analyses (see e.g., ...). To us, non-independence of interactions is not necessary when considering a network. All that is essential is the endeavour to better understand a community of interacting species, which our study does aim to do.

	10. l.252: not clear. Why this choice?

@@

		\textbf{R:} We have expanded the description of the reasoning behind our choice of prior and hope that the following is clearer:

		Lines 320-324:

		\begin{quotation}
			As we lack a trait-based model or similar published network, we will use data from a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset to inform our prior distribution. This simulates an empirical Bayes model using a pilot site to inform the prior distribution. A site in the middle of the geographic distribution was chosen in order to minimise bias towards species at any geographic extreme.
		\end{quotation}

	11. l.259: not clear

@@

		\textbf{R:} We have expanded our explanation of how mis-matched priors can give unrealistic results. We hope that the following is clearer:

		Lines 324-326:

		\begin{quotation}
			To demonstrate how a poor choice of prior can give unreasonable posterior distributions, we repeated our analyses using priors derived from a much smaller system (\emph{Appendix S7}).
		\end{quotation}

	12. Why connectance and nestedness?

@@

		Lines XX-XX:

		\begin{quotation}
			the total number of co-occurrences was generally low (mean=3.87, median=2; Fig. 2A). The bulk (92.24\%) of these co-occurring species pairs were never observed interacting. Of those pairs that did interact, the incidence of interaction was also low (mean=4.04, median=2; Fig. 2B) and was lower than the number of observed co-occurrences (Fig. 2C).
		\end{quotation}

	15. What does higher nestedness in the observed networks mean? How is it possible? [done]

		\textbf{R:} Nestedness being higher in the observed networks simply means that the additional interactions predicted by our model tend not to be between generalists and specialists and, as such, do not contribute strongly to nestedness. This is actually somewhat intuitive - ``specialists'' in the observed data are exactly those species for which we are most likely to be missing interactions, and interactions between specialists and the most likely to be predicted to occur but not have been observed. Due to the tight word limit, we do not have space to discuss this extensively in the manuscript but have added brief interpretations in the results.

@@

		\begin{quotation}
			Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig. 5C), indicating that the posterior webs include many more interactions between specialists than the observed network. In addition, the stronger the detection filter, the farther apart were the nestedness of the observed and posterior webs. This suggests that the interactions included in the observed network are not a random subset of those included in the posterior webs.
		\end{quotation}

\clearpage

% ----------------------------------------------------------------------
% ----------------------------------------------------------------------
{\Large \bf Reply to Referee \#3}
% ---------------------------------------

	The Reviewer commented that our paper is, overall, very good and ``makes an important contribution'' as ``a very nice attempt to show the broader community that the Bayesian approach is not so complex and has many advantages``. We are glad that the Reviewer agrees about the importance of this message and appreciate his/her suggestions to improve the manuscript. We have taken care to add references and clarify the introduction, as well as to state explicitly that we are emphatically not suggesting that anyone sample with lower effort/intensity than they otherwise would. We considered the benefits of high-quality sampling to be so self-evident that it did not occur to us that our manuscript could be read as suggesting that extensive sampling is not worthwhile. We thank the Reviewer for pointing out the potential for confusion over this point and hope that it is now clear that Bayesian analyses are a complement to, not a replacement for, high-quality sampling. Below we address each of the Reviewer's suggestions (response preceded with \textbf{R:}) in detail.

	1. Add more references to the literature

		\begin{refquote}
		1.      The simplest – do a better job of acknowledging what else has been done in the field – much of which has actually been done by the authors and their collaborators.  Given that they know there work I won't point that out (but they are under-siting this literature a bit) but they could consider Graham and Weinstein on-line early 2018 (I realise that this was just out when the author's submitted but it has some very similar messages) and the empirical example of Weinstein and Graham in Ecology letters 2017.  I don't think this would in any way diminish the importance of the current paper because I think the challenge in network ecology is to get people to use better quantitative methods.
		\end{refquote}

		\textbf{R:} We thank the Reviewer for stressing the need to further acknowledge previous work in the field. As this was also emphasised by other reviewers, we have taken this carefully \emph{ad notam} and expanded our references to earlier work as much as possible given length restrictions. We have taken particular care to add references to Graham/Weinsten papers as two of the reviewers suggested work by these authors. We hope that the introduction now presents a more thorough sample of previous work, remembering that our manuscript is not intended to be a comprehensive review.

@@

		\begin{refquote}
		Line 7.  It is certainly true that most networks are snapshots in time but there is a growing realisation – including some nice examples (including those by the authors) that address this issue.  Maybe what you want to say is that we know that networks should not be considered static but we lack the tools – or ability to collect data – or whatever you think is the cause – to correct this situation. 
		\end{refquote}

		\textbf{R:} When revising the manusript we removed line 7 and no longer refer to networks as snapshots.

		\begin{refquote}
		Line 30.  There are several conceptual and empirical attempts to consider detection probability – why aren't these cited (work by Bartomeus comes to mind).\\
		\end{refquote}

@@

		\begin{refquote}
			Line 36.  I certainly see value in the approach and the general ideas of these authors in particular but they should acknowledge the work that has been done by themselves and others!\\
		\end{refquote}

		\textbf{R:} We have rephrased the end of this paragraph to mention previous predictive models dealing with uncertainty in interaction matrices. As said, we have done our best to improve our coverage of previous work, within the limits offered by the current format.

		\begin{refquote}
		Line 89.  In Weinstein and Graham (Ecology Letters) the processes modelled were trait matching (which you place in interaction uncertainty) and abundance (which is perhaps your process uncertainty??).  I find myself quite confused based on how you describe things in this MS (See text above) and how you cite the literature.
		\end{refquote}

		\textbf{R:} We have revised this section and now no longer refer to the specifics of Weinstein and Graham at all. Instead, we discuss repeated sampling in an appendix dedicated to the question of whether sampling is useful (of course it is) and whether it can completely solve problems of uncertainty in ecological networks (almost certainly not). We hope that this is less confusing.

		\begin{refquote}
		Line 148.  Please note that a paper with a very similar aim was recently published (Graham and Weinstein).  This does not to diminish the value of this study in any way, as multiple perspectives on quantitative solutions in network ecology are urgently needed..... but the other work should be considered. 
		\end{refquote}

		\textbf{R:} We had not seen the Graham and Weinstein paper when we first submitted our manuscript, but now cite it in the introduction. We have also revised this section in hopes of making the uniqueness of our framework (its simplicity and adaptability) clear. % Dom and Tomas have a paper that also addresses this, but I'm not quite sure which one (you're both too productive!)

		\begin{refquote}
		Line 288.  I am pretty sure this idea is in the literature several times and should be cited.  Isn't this the same as drawing a probability of interaction from a distribution where the distribution of each interaction is an output of the Bayesian method?
		\end{refquote}

@@

		\textbf{R:} Yes, that is exactly the idea. We are also sure that this is a common approach and therefore hadn't cited it (in the same way one would not be likely to cite the prior users of common statistical tests). We have added a citation to~\citet{Vazquez2005,Guimera2009} as two examples and hope that this is sufficient.

		\begin{refquote}
		Line 352 – 358.  Citations are needed in this section as this has been suggested before.
		\end{refquote}

		\textbf{R:} Most of these lines refer specifically to our results, making it somewhat difficult to add citations. We have added citations where possible and rephrased this section to make it clearer when we are referring to work done in the present manuscript.

	2. Clarify confusing terminology

		\begin{refquote}
		2.      Provide more clarity in descriptions making sure to consider how terms and ideas have been used previously.  Two things come to mind – the use of terms and distinction between interaction and process uncertainty; and the somewhat contradictory sounding statements about if sampling more is actually good.

		Line 86.  So, similar factors (i.e., trait matching) can be used to detect different kinds of uncertainty.  Should this be stated?  You might also consider a different word that process as ``observation models'' and ``process models'' are commonly used terms in Bayesian stats and in this case ``process'' often considers what you call ``interaction''.  There are some interesting to attempts to model co-evolution that consider similar ideas (i.e., a barrier to interaction and then trait-matching; but maybe outside of the scope of this MS). While I appreciate that your naming has merit, I think if your hope is that more ecologists use these methods then the terminology should be consistent across papers/approaches to the greatest extent possible.
		\end{refquote}

		\textbf{R:} We have revised this section of the introduction to both avoid introducing rigid terminology and make it clear that our model is not concerned with partitioning different sources of variation (indeed, we state that in many cases this is not possible using empirical data). Hopefully this will discourage readers from getting bogged down in trying to isolate which external factors cause which types of uncertainty (there is almost certainly overlap - e.g., bad weather could both reduce the probability that species will be active and interact and the probability that an interaction is observed if visibility is poor). We have also added a section (beginning line 117) referring to ``forbidden links'' which addresses overlap between the questions of whether species can interact (which we had previously called interaction uncertainty) and whether they do interact at a particular site (previously process uncertainty). We hope that this addition clarifies the agreement of our manuscript with previous works listing sources of uncertainty.

			\begin{quotation}
        \textbf{Forbidden links}

            Both whether species can ever interact and whether they interact at a particular place and time have been discussed in the context of ``forbidden links``~\citep{Jordano2016}. In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc. are considered ``structural zeros'' that cannot be observed~\citep{Jordano1987,Jordano2016}. We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}. In such cases, links which are impossible due to physiological constraints remain forbidden but links previously ``forbidden'' by spatio-temporal mismatch could potentially occur. 
      \end{quotation}

	3. Introduction of the case study seems off-topic and illogical.

		\begin{refquote}
		3.      The set up (introduction) to the case study is quite odd and somehow seems off topic – or at least not logical based on what the reader has read up to that point.
		\medskip
		Line 240.  I found the justification for the system a bit odd.  Is the goal to show the gaps in sampling or to apply the model described thus far to consider the 3 different types of uncertainty outlined?  At this point the reader is confused about the goal...
		\medskip
		Line 249.  The statement about training data is redundant with what is stated above – adjust writing.
		\end{refquote}

		\textbf{R:} We have expanded our introduction of the case study (beginning line 295) to make it clear that we are using the highest-quality empirical network we can find as even such networks have uncertainty about unobserved interactions. This relates back to our point that urging increased sampling effort is not likely to solve problems of uncertainty as long as sampling is limited in the number of methodologies that can be applied, biased towards abundant or easy-to-identify species, restricted to particular spatial sites and/or environmental conditions (if the network is intended to be more general), or all of the above. Given budgetary constraints, it is extremely likely that empirical ecologists cannot sample as intensively and extensively as they would like and therefore some uncertainty is likely to remain. We repeat this point in the discussion to ensure that the case study is relevant. We have also clarified our statement that a strict application of Bayesian statistics does not allow empirical priors, but that they are an option for researchers that are more concerned about matching their prior to their study system than with strict formalism (lines 296-293). As Reviewer 1 points out, this is somewhat controversial and we feel it is important to note the potential objection.

		\begin{quotation}
		  \subsection*{An empirical example}

### 2019-01-16 manuscript/reply_to_reviewers.tex

		      To illustrate the process of constructing a Bayesian network to quantify uncertainty about interactions, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S5} for details). 
		      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, there were many pairs of species which were rarely or never observed together and about which we therefore have high uncertainty about interaction probabilities (Fig.~\ref{histograms}). Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb. 
		      % To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions. 
		      We calculated an empirical prior and computed the posterior distribution of the probability of an as-yet-unobserved interaction being feasible ($\lambda_{ij}$). We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S6} for \emph{Salix}-galler results).
		\end{quotation}

	4. Misunderstanding of our point about sampling effort

		\textbf{R:} We believe that the Reviewer has  misunderstood the point of our comments on sampling effort. Several of their comments suggest that they believe that we are advocating for reducing sampling effort. This is emphatically not the case. Rather, we assumed that field researchers already sample to the maximum extent possible given their time and resource constraints and so a call to ``sample more'' would not be helpful. Increased sampling can reduce some sources of uncertainty, but is unlikely to remove all uncertainty and so is not a complete solution. We now address this explicitly in an appendix (Appendix S2)  dedicated to the potential for sampling effort to reduce uncertainty about interactions. Below, we address the Reviewer's sampling-related comments one by one.

@@

		\begin{refquote}
		Line 94.  I find this a very odd argument against sampling multiple times.  So, if you sample more you might see more then understand the system less?  The logic does not make sense to me. 
		\end{refquote}

		\textbf{R:} Of course sampling more does not lead to less understanding. It can, however, reveal knowledge gaps (as when a rare species is detected, revealing our ignorance of its interactions). This is not an argument against multiple sampling but a statement that increased sampling is likely to lead to the addition of more ``false zeros'' as species about which we know little are added to the network.

@@

		\textbf{R:} We are pleased that this point was clear and have made sure to include it in our revision.

		\begin{refquote}
		Line 319.  It is clear that these are large samples but if interaction among co-occurring species was greater than you need lower samples – correct?  Should this be made clear?  Otherwise, we maybe can just never get enough data!
		\end{refquote}

		\textbf{R:} We are specifically speaking about interactions which were never observed. As interaction networks tend to be sparse, there will always be many of these. If interaction frequencies were higher among species that co-occurred, then we would have fewer unobserved interactions but the sample sizes needed to be confident that an unobserved interaction does not occur would not change (perhaps our threshold for deciding to believe a zero might, which is why we provide sample sizes for several thresholds). The Reviewer has hit the nail on the head with the idea that it is extremely hard to get enough data to be sure about every interaction. This is why prior knowledge can be so useful!

		\begin{refquote}
		Line 338 to 342.  Throughout I am confused if the authors suggest more sampling is good or bad...  At the end of the paragraph it seems it isn't so great to sample more because you end up with these annoying ``0'' values...??????
		\end{refquote}

		\textbf{R:} In our revised manuscript, we have collected our discussion of sampling into a dedicated appendix and added several explicit statements that high-quality sampling can reduce some sources of uncertainty. We hope that it is now clear that sampling is very important but cannot completely eliminate uncertainty (except perhaps in some very species-poor and unusually static systems, but these are certainly rare). As to adding more zeros than ones specifically, this is only ``bad'' in the sense that it gives us more high-uncertainty cells in the interaction matrix. We take the view that it is better to have ``known unknowns'' than ``unknown unknowns'' and it is certainly better to know about more of the species in a community than fewer, but finding a single individual of a rare species will not reduce uncertainty in the web. We have added a line in \emph{Appendix S2} specifically to address this.

@@

		\begin{quotation}
			we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig. 2C). While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the interaction matrix. Note that it is better to identify the set of potential interactions than to miss a species, so sampling effort should not be reduced in order to exclude rare species.
		\end{quotation}

	5. Eliminate redundant ``because'' on line 23

		\textbf{R:} Done.

	6. Reduce repetition of inevitable uncertainty

		\begin{refquote}
		Line 73, 87.  Maybe the idea that some uncertainty is ``inevitable'' should not be repeated in multiple sections.  Either find a different way of saying it – or state it in your introductory paragraph and then don't keep repeating.
		\end{refquote}

		\textbf{R:} We have rephrased the manuscript and the word ``inevitable'' no longer appears. We hope that the current phrasing is less repetitive.

	7. Why not always model probabilities of co-occurrence?

		\begin{refquote}
		Line 142.  But shouldn't you model the probability of two species co-occurring?  The authors have a paper doing this.... Is that not a good idea?
		\end{refquote}

		\textbf{R:} Modelling the probability of co-occurrence is an option for many systems (e.g., aquatic food webs where ranges of fish species are fairly well-known, as in~\citet{Gravel2013}). It may also be possible to separate the probability of observing an interaction at a particular location into a metaweb component (the focus of the current manuscript) and a co-occurrence probability as in~\citep{Gravel2018}. This addresses the question of interaction probabilities at specific locations, however, in contrast to our focus on metaweb interaction probabilities.

		In some systems, however, the factors affecting probabilities of co-occurrence may not be known. We therefore cannot suggest modelling co-occurrence as a panacea. Instead, we now emphasise that co-occurrence probabilities are one thing that could be included in a prior (section beginning line 231). [[Add a ref to Gravel 2018?]]

		The fact remains that a lack of observed interactions between species which do not co-occur tells us nothing about whether these species \emph{could} interact if they should begin to co-occur (e.g., following a range shift). Following the Reviewer's suggestion, we have revised our manuscript to clarify our terminology. In particular, we have taken care to specify which level of uncertainty we are addressing at different points in the manuscript. We hope that this will remove some of the confusion about whether or not modelling different components of uncertainty/sampling more is a good idea.

	8. Issue of testing hypotheses based on inputs into models

		\begin{refquote}
		Line 121.  I think one of the reason non-Bayesians' are not comfortable with the approach is that if you put in prior information on something like trait matching and test for trait matching and then discover trait matching is important – what does it mean?  Maybe this is too obvious (I realise there are tons of papers on how to choose priors) but I wonder if it is worth explaining (would a box or something be worthwhile?  I leave it up to the authors/editor)?  Maybe the issue could be acknowledged and an appropriate paper cited?
		\end{refquote}

		\textbf{R:} Following suggestions by this Reviewer and another, we have substantially expanded our discussion of different options for priors (including the trait-based and co-occurrence models the Reviewer points out). We have also added an explicit statement that researchers wishing to test the influence of a particular trait (for example) should \emph{not} include that trait in their prior (lines 252-255). We hope that this statement, and the expanded discussion of different types of priors more generally, allay the Reviewer's concerns.

		\begin{quotation}
			Also note that researchers wishing to test whether a particular trait influences interaction probabilities should either exclude that trait from their prior or model the network using priors which include and exclude the trait of interest (as in~\citet{Weinstein2017,Weinstein2017a}).
		\end{quotation}

	9. Redundancy in line 235

@@

		\textbf{R:} The redundant line has been removed. Thank you for pointing this out.

	10. Unsure about the point of filtering networks

		\begin{refquote}
		Line 295 to 302.  I would think that this second step (i.e., filtered networks) is to explore sampling not to determine how networks will be influenced by uncertainty?  Do you need the filtering step to evaluate uncertainty (as written it seems that this is the case)?
		\end{refquote}

		\textbf{R:} The filtering was intended to show how uncertainty likely warps our current understanding of network properties like connectance. If we do not observe 20-50\% of the interactions in a network, then many network properties in the published literature will be inaccurate. Even worse, networks compiled under different levels of uncertainty (e.g., species with more or less variable traits, or studies with multiple sampling methods versus only one) or with different sampling efforts will have network structure metrics that are inaccurate to different degrees. Filtering networks in the way that we do could give an idea of how many networks are missing, but we do not think it is necessary to evaluate uncertainty (we believe that examining the posterior distributions directly is a better approach there). Due to length restrictions, we have moved this anslysis to an appendix (\emph{Appendix S10}) and haverephrased these lines to emphasise that the filtered networks are intended to demonstrate the consequences of uncertainty more than anything else.

@@

		\begin{quotation}
			Measures of network structure which are based on empirical networks that are missing interactions may differ substantially from the values that would be obtained if detection certainty and variation in interactions over space and time could be removed. To demonstrate this, we created a suite of filtered networks for each posterior network. 
		\end{quotation}

	11. Scepticism about sampling requirements to be sure interactions do not occur

		\begin{refquote}
		Line 361.  I find the statement that 30-50 individuals need to be evaluated a bit strong.  This statement is based on this study – are all systems like the gall system?  If species are specialised or bound to interact for some other reason (i.e., co-occurring when there are few other resources) wouldn't you need to observe fewer individuals?  The point of the method is that you can estimate how many individuals are needed.... This is great!  But given that this can be estimated from any given system why give a value from one system and state that is what is required?  It defeats the point of the very nice method proposed...??
		\end{refquote}

@@

		\textbf{R:} The point of our method is not actually to quantify the amount of sampling needed. Although the ideal sampling effort \emph{can} be calculated using the framework we put forward (as we demonstrate), the real point is to quantify how uncertain we are that an interaction we do not observe really does not occur. Given this, we do not think that recommending uncertainty be explicitly stated undermines our point.

		The Reviewer's suggestion that we might need fewer samples for species that are ``specialised or bound to interact for some other reason'' reflects a very strong prior. In this case, yes we would need fewer samples for the species concerned. With sufficiently strong priors, it is not necessary to sample at all! For example, in most food webs it is assumed that basal resources will never consume prey even if a given resource and a given animal are never observed co-occurring and it is generally accepted that there is very low uncertainty about these zeros. In many cases, the assumptions involved in excluding interactions are less clear-cut and different researchers may disagree about which species are ``bound to interact'' (or not to interact). The concept of pollination syndromes is one example - many flower visitors are less rigidly specialised on particular flower types than initially thought~\citep{Ollerton2009}. To address such ``forbidden links``, we now suggest that researchers explicitly state both the uncertainty about data-based zeros and the assumptions by which they create structural zeros. This will allow future researchers to evaluate the uncertainty about all interactions in a network as the state of expert knowledge changes. We hope that this expanded recommendation (lines XX-XX) is clearer.

		Finally, we emphasize that the estimate of 30-50 samples does not refer to the \emph{Salix}-galler-natural enemy test system but to a much more general interpretation of the problem. Without a prior distribution and with \emph{no prior information}, as long as we assume that interaction probabilities follow a beta distribution it will take 30-50 observations of two species co-occurring to be 95-99\% confident that the species do not interact. Sampling requirements will be much less if an interaction was observed (note that in the empirical example we assume an interaction was feasible if it was observed even once).

@@

\clearpage

% ----------------------------------------------------------------------
% ----------------------------------------------------------------------
{\Large \bf Reply to Referee \#4}
% ---------------------------------------

	The Reviewer has ``been surprised how little that sampling effects have been formally considered in the analysis of networks'' and therefore feels that our manuscript makes an important contribution. Nevertheless, the Reviewer has concerns that the manuscript might not reach empirical ecologists ``because they either would not understand its relevance or would not be able to apply it practically``. We agree with the Reviewer that this would be a great shame, and appreciate their suggestions to improve the manuscript. With this revision, we hope that we have established the relevance of our method and offered enough of an explanation that empiricists will be able to apply it. Our goal is to increase access to a statistical technique which we see as complementary to high-quality field work, and we believe that the Reviewer's comments will help us to achieve this. We respond (preceded by \textbf{R:}) to each of the Reviewer's comments in detail below.

	1. Paper is poorly structured

@@

	3. Comment on weighted metrics

		\begin{refquote}
		L36ff The authors should note the value of weighted metrics in taking account of sampling biases.
		\end{refquote}

		\textbf{R:} We do not see how weighted metrics (which we infer mean metrics including interaction strength/frequencies based on the Reviewer's comment below) account for sampling biases. It seems to us that measures of interaction strength should be \emph{more} susceptible to sampling biases, not less, as abundant species are both more likely to have their interactions recorded and more likely to have these interactions recorded as strong/frequent. Of course weighted metrics have many other strengths, but these are not germane to the topic at hand. We have rephrased the introduction so that the original line 36 no longer appears, and hope that this will remove the Reviewer's objection.

		Applying our framework to quantitative networks is beyond the scope of the current study due to length restrictions. It is, however, an interesting question worthy of future consideration. With quantitative interactions, the problem of true and false zeros disappears. However, there will now be a great deal of uncertainty about the observed interactions as we must now estimate variability in interaction frequencies. There is a significant trade-off here, and whether quantitative or qualitative networks are better-suited to acknowledging uncertainty in species interactions remains a very open question.

	4. Request for extension to weighted networks

@@

		\begin{refquote}
		L45 It is a shame not to give some idea of how the method could be extended (or is this the intention of the authors?). For empirical analysis of networks it is rare to use binary networks given the value of weighted networks for taking account of sampling biases. Indeed, I am much less concerned about whether an interaction never occurs, and much more concerned with the frequency of occurrence.
		\end{refquote}

		\textbf{R:} As stated above, we do not agree that weighted networks reduce sampling biases. Moreover, we disagree that it is rare to use binary networks as most food webs (for example) are still binary. It takes an even greater sampling effort to quantify interaction strengths than the presence and absence of links, so for species-rich systems in particular there simply are not many high-quality weighted networks published. Moreover, as the Reviewer mentioned, empirical ecologists may already struggle to apply a Bayesian framework using qualitative data. We therefore opted not to extend our framework in this manuscript and leave this as an area for future work.

	5. Description of causes of uncertainty poorly integrated with the case study

@@

		\begin{refquote}
		L50 This is a nice and clearly explained description of the problem that many network ecologists ignore, or are unaware of.
		Section from L50. This section is valuable, but had very weak links with the empirical analysis later in the paper. For instance in the example of the gall-formers, there was not formal discussion about the different sources of uncertainty. 
		\end{refquote}

		\textbf{R:} As we state in the section \textbf{Estimating uncertainty}, we usually cannot distinguish different sources of uncertainty in empirical data. Those studies which attempt to do so (e.g.,~\citet{Graham2018}) remove process uncertainty by assuming constant interaction probabilities during a short, intense sampling period and also assume that we know the true set of feasible interactions. This may be the case for Graham and Weinstein's relatively small and well-studied system but is not likely to be true for systems containing hundreds of species, systems containing recently-arrived species, systems just beginning to be studied, etc.

		To make this clearer, we have rephrased this section and added a line (lines 61-68) stating that we usually cannot determine the cause of all the zeros in an interaction matrix (we can identify obviously unfeasible interactions, but likely cannot say whether a zero for a rare species is because we did not observe enough individuals, there were not enough individuals to perform a particular interaction, or because the interaction is actually unfeasible). We hope that this revision makes it clearer that the description of different sources of uncertainty is a conceptual guide only.

		\begin{quotation}
			While an observed link definitely occurred (assuming correct identification of the species involved), a given link may not be observed for many reasons, \emph{whether or not it truly occurred} (Fig.~\ref{conceptual_fig}). Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction was not observed \emph{post hoc}. The detection of any interaction is a stochastic process subject to many levels of uncertainty. As a conceptual guide, we describe three nested levels of uncertainty that roughly address the questions: ``Could species $i$ and $j$ interact?", ``Did they interact during sampling?", and ``Did we observe the interaction?"
		\end{quotation}

		For the Reviewer's interest, some of the authors in the present manuscript investigated environmental variables and co-occurrence as potential sources of variance and found that most of the variability was driven by co-occurrence. This is analogous to the effect of abundance, but at a larger scale (where many abundances are locally 0). These analyses are described in [[Add ref!!!]]

	6. Process uncertainty poorly defined.

		\begin{refquote}
		L76ff `Process uncertainty' is not defined. The simplistic example of interaction uncertainty (fish eating a cactus) does not help the reader understand the detail of what is meant by `interaction uncertainty'. The two examples of `local constraints' (weather and habitat) are operating on completely different temporal scales (note – it is defined differently in L109). I would regard the issue of weather as much closer to detection uncertainty (e.g. for a pollinator, it would be likely to be interacting if the weather was better), whereas the issue of habitat is closer to the authors' `interaction uncertainty' (the species don't interact because they are not, or never, co-occurring in a habitat). Also if the species occur in different habitats then with an appropriate spatial scale of sampling then they do not co-occur – so the issue seems redundant. [[I suspect that the authors are thinking of a meta- or master network in much of their study, but this is not clear (or I have misunderstood and it needs to be explained better), i.e. the predicted presence of an interaction is not the presence of an interaction at the local site (taking detection and process uncertainty into account) but the ability to assess `interaction uncertainty'.]][[This is a bit separate from their issue]]
		\end{refquote}

		\textbf{R:} As our manuscript is not concerned with partitioning sources of uncertainty, we felt it was unproductive to get bogged down in a debate over the precise definitions of process vs. interaction uncertainty and which external influences might contribute to which sources (there is enough overlap that simple statements such as ``bad weather increases process uncertainty'' are, at best, incomplete). To remove this problem, we have rephrased the introduction and discussion to refer to the questions of whether two species \emph{can} interact under ideal conditions and whether they \emph{do} interact at a given site and time. We hope that this reframing, and the addition of clear statements that our framework is not intended to separate different sources of uncertainty, will remove the Reviewer's confusion.
